### 2024-03-11 doc/15yrsChange.Rmd
Update Author/Affiliations and Add Citation Checklist

Rachel Hoffman

Krystal Bagnaschi

Iris Kennedy

Erin MacMonigle

Caroline Troy

Cameron Dow

@@

Jen Jordan

Lukas Magee

David Mitre

Christopher Pate

Jess Shue

William McShea

@@

1. Conservation Ecology Center; Smithsonian's National Zoo & Conservation Biology Institute; Front Royal, Virginia 22630, USA

@@

>>>>

Rachel Hoffman^1^

Krystal Bagnaschi^1^

Iris Kennedy^1^

Erin MacMonigle^1^

Caroline Troy^1^

Cameron Dow^1,3^

@@

Jennifer Jordan^1,4^

Lukas Magee^1,5^

David Mitre^2^

Christopher Pate^1^

Jessica Shue^6^

Norman A. Bourg^1^

William J. McShea^1^

@@

1. Conservation Ecology Center, Smithsonian's National Zoo & Conservation Biology Institute, Front Royal, Virginia 22630, USA

@@

3. Department of Biology, West Virginia University, Morgantown, West Virginia 26506, USA

4. Department of _____, George Mason University, Fairfax, Virginia 22030, USA

5. School of Forest, Fisheries and Geomatics Sciences, University of Florida, Gainesville, Florida 32603, USA

6. Forest Global Earth Observatory, Smithsonian Environmental Research Center, Edgewater, Maryland 21037, USA
